### 2012-11-16 doc/progress_plan/report.tex
Finished compiling appendicies

\usepackage{fullpage}

%use the listings package
\usepackage{listings}
%use the English language
\usepackage[english]{babel}
%use graphics
\usepackage{graphicx}
%use wrap figures
\usepackage{wrapfig}
%geometry stuffs
\usepackage{lscape}
%use natbib bibliography package
%\usepackage[numbers]{natbib}
%use harvard bibliography package
%\usepackage{harvard}	
%use captions
\usepackage{caption}
%use multi-row tables
\usepackage{multirow}
\usepackage{url}
\usepackage{subcaption}

@@

\subsubsection{Social Citation and Recommendation Engines}
Social citation and recommendation engines also provide a partial solution to
the `information overload' problem.  Services like Goodreads
(\url{http://www.goodreads.com/}) and CiteUlike
(\url{http://www.citeulike.org/}) allow you to register your interest in
specific authors and subjects. This allows the sites to build up a profile of
the sorts of materials that you might be interested in and provide lists of
recommendations as in Figure \ref{social_indexes}.

@@

SAPIENTA for Python also relies upon a package called CRFSuite which implements
Conditional Random Fields, a method for segmenting and labelling sequence
data\cite{CRFsuite}. This library did not compile properly on the test
environment and its creator had to be contacted via a mailing list (See
Appendix \ref{sec:crfletter}. After a few days, the owner responded and the
library was compiled successfully.

@@

\appendix
\section{User Interface Designs}
\label{sec:ui_designs}

\section{System Process Diagrams}
\label{sec:system_diagrams}

\section{Email for CRFSuite}
\label{sec:crfemail}
\input{crfletter}

\section{Project Timeline}
\label{sec:timeline}

\section{Project Wiki}
\label{sec:wiki}

\bibliographystyle{IEEEannot}
\bibliography{report}

>>>>

\usepackage{fullpage}
\usepackage{pdfpages}
%use the listings package
\usepackage{listings}
%use the English language
\usepackage[english]{babel}
%use graphics
\usepackage{graphicx}
%use wrap figures
\usepackage{wrapfig}
%geometry stuffs
\usepackage{lscape}
%use natbib bibliography package
%\usepackage[numbers]{natbib}
%use harvard bibliography package
%\usepackage{harvard}	
%use captions
\usepackage{caption}
%use multi-row tables
\usepackage{multirow}
\usepackage{url}
\usepackage{subcaption}

@@

\subsubsection{Social Citation and Recommendation Engines}
Social citation and recommendation engines also provide a partial solution to
the `information overload' problem.  Services like Goodreads
(\url{http://www.goodreads.com/}) and CiteUlike
(\url{http://www.citeulike.org/}) allow you to register your interest in
specific authors and subjects. This allows the sites to build up a profile of
the sorts of materials that you might be interested in and provide lists of
recommendations as in Figure \ref{fig:social_indexes}.

@@

SAPIENTA for Python also relies upon a package called CRFSuite which implements
Conditional Random Fields, a method for segmenting and labelling sequence
data\cite{CRFsuite}. This library did not compile properly on the test
environment and its creator had to be contacted via a mailing list (See
Appendix \ref{sec:crfemail}. After a few days, the owner responded and the
library was compiled successfully.

@@

%include document appendix
\input{appendix}
